Figures

### 2016-01-02 scripts/figures.Rmd
makes all figures

```{r, phred_mapq filter}
ggplot(subset(sig.df,gc==5 & category %in% c(T,F)),aes(x=Phred,y=MapQ,color=category))+geom_point()

sig.df<-subset(sum.df,p.val<0.001)

@@

## 4) Read position

```{r,read_pos}
ggplot(sig.df,aes(x=pos,y=Read_pos,color=category))+geom_point()+facet_wrap(~chr)
ggplot(subset(sig.df,gc==5),aes(x=pos,y=Read_pos,color=category))+geom_point()+facet_wrap(~chr)

@@

>>>>

```{r, phred_mapq filter}
sig.df<-subset(sum.df,p.val<0.001)

ggplot(subset(sig.df,category %in% c(T,F)),aes(x=Phred,y=MapQ,color=category))+geom_point(alpha=0.5)+facet_wrap(~gc)

@@

## Figure 4

### Read Position
```{r,read_pos}
ggplot(sig.df,aes(x=pos,y=Read_pos,color=category))+geom_point()+facet_wrap(~chr)
ggplot(subset(sig.df,gc==5),aes(x=pos,y=Read_pos,color=category))+geom_point()+facet_wrap(~chr)

@@

cut.read.df<-subset(cut.df,Read_pos>32 & Read_pos<94)

h.cut.read.df<-hiseq.roc(cut.read.df,possible_tp,possible_vars)

ggplot(subset(h.cut.read.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))

h.cut.read.table<-hiseq.roc.table(cut.read.df,0.001,possible_tp,possible_vars)
knitr::kable(subset(h.cut.read.table,gc==5))
```
### Lofreq out of the box
```{r,lofreq}

lofreq.df<-read.csv("../data/process/2015-6-23/lofreq/all.removed.mapq_vcf.vcf_csv.csv")

lofreq.df$p.val<-lofreq.df$QUAL # to make the roc based on the quality scores given by lofreq

lofreq.roc<-hiseq.roc(cut.df,possible_tp,possible_vars)

ggplot(subset(lofreq.roc,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("1-Specificity (adjusted)")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))

#lofreq claims no further monkey bussiness is needed to we'll just make a table with all its output
ddply(lofreq.df,~Id,summarize,gc=gc[1],exp.freq=exp.freq[1],TP=length(which(category==T)),FP=length(which(category==F)))->lofreq.table
lofreq.table<-lofreq.table[order(lofreq.table$exp.freq,decreasing = T),]

knitr::kable(subset(lofreq.table,gc==5,select=c(exp.freq,TP,FP)))

```
### Frequency accuracy
```{r, frequency_accuracy}
# Here we'll just be using

## Frequency
cut.read.sig.df<-subset(cut.read.df,p.val<0.01)
medians<-ddply(subset(cut.read.sig.df,category==T ),~exp.freq+gc, summarize, median=median(freq.var))

# ac_freq<-ggplot(subset(sum.df,category==T),aes(x=exp.freq,y=freq.var,fill=as.factor(exp.freq)))+facet_wrap(~gc)

#cut.read.sig.df$exp.freq<-as.factor(cut.read.sig.df$exp.freq)
#cut.read.sig.df$exp.freq <- factor(cut.read.sig.df$exp.freq, levels = rev(levels(cut.read.sig.df$exp.freq)))

ac_freq<-ggplot(subset(cut.read.sig.df,category==T & gc=="5"),aes(x=exp.freq,y=freq.var,fill=factor(exp.freq,levels=rev(levels(as.factor(exp.freq))))))

ac_freq<-ac_freq+geom_dotplot(binaxis = "y", stackdir = "center",dotsize=1)+scale_fill_brewer(palette="Set1")

ac_freq<-ac_freq+scale_y_log10(limits=c(0.001,0.1),breaks=c(0.001,0.002,0.005,0.01,0.02,0.05,0.1))#+theme(axis.text.y = element_text(colour = c("red","chartreuse4","black","chocolate2","azure4","blue","black"),face="bold"))
ac_freq<-ac_freq+scale_x_log10(limits=c(0.001,0.1),breaks=c(0.001,0.002,0.005,0.01,0.02,0.050,0.1))#+theme(axis.text.x = element_text(colour = c("red","chartreuse4","black","chocolate2","azure4","blue","black"),face="bold"))
ac_freq<-ac_freq+geom_abline(intercept = 0, slope = 1,linetype=2,size=1)
ac_freq<-ac_freq+xlab("Expected Frequency")+ylab("Measured Frequency")+theme(legend.position="none")

ac_freq<-ac_freq+geom_point(data=subset(medians,gc=="5"),mapping=aes(x=exp.freq,y=median),shape=95,size=30)
ac_freq
```

## Figure 5 Lower inputs

```{r,roc lower_inputs}
ggplot(subset(h.cut.read.df,gc==4),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))

ggplot(subset(h.cut.read.df,gc==3),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))
```

### Duplicates

```{r,duplicates}
sum.df<-read.csv("../data/process/2015-11-14/Variants/all.sum.csv",stringsAsFactors = F,comment.char = "#")
pat<-"([0-9]+)_([0-9]+)"
mutate(sum.df, exp.freq = sub(pat,"\\1",Id),
       dup = as.numeric(sub(pat,"\\2",Id)),
)-> sum.df
mutate(sum.df,exp.freq=ifelse(test = grepl("0",exp.freq),yes=as.numeric(exp.freq)/1000,no = as.numeric(exp.freq)/100))->sum.df

sum.df<-subset(sum.df,Id!="PC") # remove the plasmid control that was run

sum.df<-mutate(sum.df,category=mutation %in% true_snv$mutant) # add Column for True and false variants
sum.df$category[sum.df$mutation %in% wt_mut]<-"wt"

cut.df<-subset(sum.df,Phred>35 & MapQ>30 & Read_pos<94 & Read_pos>32)

dups<-ddply(cut.df,~exp.freq+mutation,summarize,freq1=freq.var[1],freq2=freq.var[2],p.val1=p.val[1],p.val2=p.val[2],category=category[1],Id=Id[1])
dups$freq2[is.na(dups$freq2)]<-0
dups$p.val2[is.na(dups$p.val2)]<-1

dups<-mutate(dups,p.val=pmax(p.val1,p.val2),Id=gsub(pat,'\\1',Id),gc=4)

dups.roc<-hiseq.roc(dups,possible_tp,possible_vars)

ggplot(dups.roc,aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))

dups.table<-hiseq.roc.table(dups,0.001,possible_tp,possible_vars)
knitr::kable(subset(dups.table))
